Stat 400 Project

### 2021-12-08 Stat 400 presentation.Rmd
Added new graphs and cleaned up a bit

```{r}
library(tidyverse)
library(ggplot2)
library(boot)
```

## Plot of infected people with bootstrap

\tiny
```{r, echo = FALSE, output = TRUE}

starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

- Step Function
  ![Sample](/cloud/project/image.jpg)

@@

@@

\tiny
```{r, echo=TRUE}
get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
  #Create data frame to store samples
  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
  samps <- data.frame(samps)

@@

## Boostrap plot of infected people

@@

#Testing
n=50
y <- simulator(n,100,10,10,2,1)
x <- 0:n

#bootstrap
mean_func <- function(daytuh, idx) {
  mean(daytuh[idx])
}

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, 1] <- ci_obj$percent[4]
    ci_df[i, 2] <- ci_obj$t0
    ci_df[i, 3] <- ci_obj$percent[5]
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
  }
return(ci_df)
}

plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
```

## Boostrap

```{r, echo = F}
library(boot)
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

#Testing
df <- starting_vals(1000, 2, 1, 1)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
new_status <- infection_status(coords, 8)

set.seed(400)
n=50
y <- simulator(n,100,10,10,2,1)
x <- 0:n

#bootstrap
mean_func <- function(daytuh, idx) {
  mean(daytuh[idx])
}

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, 1] <- ci_obj$percent[4]
    ci_df[i, 2] <- ci_obj$t0
    ci_df[i, 3] <- ci_obj$percent[5]
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i], samps[1, i])}
  }
return(ci_df)
}

plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)

daily_cases <- y
boot.case <- boot(daily_cases, mean_func, 2000)

plot(boot.case)

@@

>>>>

```{r,include=FALSE}
library(tidyverse)
library(ggplot2)
library(boot)
```

```{r, echo=FALSE, results='hide'}
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

@@

## What We are Trying to Simulate

- Step Function
  <!-- ![Sample](/cloud/project/image.jpg) -->

@@

\tiny
```{r, echo=TRUE}
mean_func <- function(daytuh, idx) {
  mean(daytuh[idx])
}

@@

## Plot With Bootstrap 95% CI, 100 subjects

@@

plot_dat <- get_bootstrap_cis(days=150, num_subjects=100, x_dim=20, y_dim=20, I_0=1, inf_dist=1, sample_size=20)

ggplot() +
  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
```

## Plot With Bootstrap 95% CI, 100 subjects

\tiny
```{r}
plot_dat2 <- get_bootstrap_cis(days=150, num_subjects=200, x_dim=20, y_dim=20, I_0=1, inf_dist=1, sample_size=20)

ggplot() +
  geom_line(aes(x=1:151, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:151, y=plot_dat2[ ,2])) +
  geom_line(aes(x=1:151, y=plot_dat2[ ,3]), linetype = 2, color = 'red') +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

@@

## 'Flatten the Curve' - Pseudo Vaccination Effect

\tiny
```{r}
ggplot() +
  geom_line(aes(x=1:151, y=plot_dat[ ,2]), color='red') +
  geom_line(aes(x=1:151, y=plot_dat2[ ,2]), color='blue') +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
```

## Pseudo Mask Effect

\tiny
```{r}
plot_dat3 <- get_bootstrap_cis(days=150, num_subjects=100, x_dim=20, y_dim=20, I_0=1, inf_dist=0.5, sample_size=20)

ggplot() +
  geom_line(aes(x=1:151, y=plot_dat[ ,2]), color='red') +
  geom_line(aes(x=1:151, y=plot_dat3[ ,2]), color='blue') +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')
```

### 2021-12-08 Stat 400 proj.Rmd
Avoiding an error
Added new graphs and cleaned up a bit

plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)

@@

```{r}
#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
mcsum
```

>>>>

plot_dat <- get_bootstrap_cis(days=50, num_subjects=3500, x_dim=100, y_dim=100, I_0=18, inf_dist=0.5, sample_size=20)

@@
